### 2021-10-20 text/outline/outline.tex
limit in c of gamma

We rewrite the attenuation fraction $\gamma$ in a way that makes it more amenable to theoretical analysis. We leverage the fact that $f$ integrates to unity and is even.
First,
\begin{multline}\label{thm:gamma_expression_1} \E\left[\hat{p}_i\right] = (1 - \pi) \left( \int_{c - \beta^g_0}^\infty f \right) + \pi \left(\int_{c - \beta_0^g - \beta_1^g}^\infty f \right) \\ = (1 - \pi) \left( \int_{-\infty}^{ \beta_0^g - c} f \right) + \pi \left( \int_{-\infty}^{ \beta^g_0 + \beta^g_1 - c} f \right), \end{multline}
 and so \begin{multline}\label{thm:gamma_expression_2} 1 - \E\left[\hat{p}_i\right] = (1 - \pi) + \pi - \E[\hat{p}_i]  = (1-\pi) \left(1 - \int_{c - \beta_0^g}^\infty f \right)  + \pi \left(1 - \int_{c - \beta^g_0 - \beta^g_1}^\infty f \right) \\ = (1 - \pi) \left( \int_{-\infty}^{c - \beta^g_0} f \right) + \pi \left( \int_{-\infty}^{c - \beta_0^g - \beta_1^g} f \right).
\end{multline}
Next,
\begin{equation}\label{thm:gamma_expression_3}
\omega = \int_{c - \beta^g_1 - \beta^g_0}^\infty f,\end{equation} and so
\begin{multline}\label{thm:gamma_expression_4}
\omega - \E[\hat{p}_i]  = \left( \int_{c - \beta^g_1 - \beta^g_0}^\infty f \right) - (1 - \pi) \left( \int_{c - \beta^g_0}^\infty f \right) - \pi \left( \int_{c - \beta_0^g - \beta_1^g}^\infty f \right) \\ = (1 - \pi) \left(\int_{c - \beta^g_0 - \beta^g_1 }^\infty f \right) - (1- \pi) \left(\int_{c - \beta^g_0}^\infty f \right) \\ =  (1 - \pi)\left(\int_{-\infty}^{\beta_0^g + \beta_1^g - c} f \right) - (1 - \pi) \left( \int_{-\infty}^{ \beta_0^g - c} f \right).
\end{multline}
Combining (\ref{thm:gamma_expression_1}, \ref{thm:gamma_expression_2}, \ref{thm:gamma_expression_3}, \ref{thm:gamma_expression_4}), we find that
\begin{multline}\label{gamma_alternative}
\gamma(\beta^g_1, c, \pi) = \frac{\pi(\omega - \E[\hat{p}_i])}{\E[\hat{p}_i](1 - \E[\hat{p}_i])} \\ = \frac{\pi \left[ (1 - \pi) \left( \int_{ -\infty}^{\beta_0^g + \beta_1^g - c} f \right) - (1 - \pi) \left( \int_{-\infty}^{ \beta_0^g - c} f \right) \right]}{\left[(1-\pi) \left( \int_{-\infty}^{ \beta_0^g - c} f \right) + \pi \left( \int_{-\infty}^{ \beta^g_0 + \beta^g_1 - c} f \right) \right] \left[(1 - \pi) \left( \int_{-\infty}^{c - \beta^g_0} f \right) + \pi \left( \int_{-\infty}^{c - \beta_0^g - \beta_1^g} f \right) \right]}.
\end{multline}
As a corollary, when $\pi = 1/2$, we have that
\begin{multline}\label{gamma_alternative_pi_half}
\gamma(\beta^g_1, c, 1/2)  \\ = \frac{\left( \int_{ -\infty}^{\beta_0^g + \beta_1^g - c} f \right) - \left( \int_{-\infty}^{ \beta_0^g - c} f \right) }{ \left[ \left( \int_{-\infty}^{ \beta_0^g - c} f \right) + \left( \int_{-\infty}^{ \beta^g_0 + \beta^g_1 - c} f \right) \right] \left[\left( \int_{-\infty}^{c - \beta^g_0} f \right) + \left(\int_{-\infty}^{c - \beta_0^g - \beta_1^g} f \right) \right]}.
\end{multline}
Recalling the definitions of $g$ (\ref{def_g}) and $h$ (\ref{def_h}), we can write $\gamma$ as
$$ \gamma(\beta^g_1, c, \pi) = \frac{g(\beta^g_1, c, \pi)}{h(\beta^g_1, c,\pi)}.$$

@@

We compute the derivatives of $g$ and $h$ in $c$, which we will need for subsequent results.

>>>>

We rewrite the attenuation fraction $\gamma$ in a way that makes it more amenable to theoretical analysis. We leverage the fact that $f$ integrates to unity and is even.
First,
\begin{multline}\label{thm:gamma_expression_1} \E\left[\hat{p}_i\right] = (1 - \pi) \left( \int_{c - \beta^g_0}^\infty f \right) + \pi \left(\int_{c - \beta_0^g - \beta_1^g}^\infty f \right) \\ = (1 - \pi) \left( \int_{-\infty}^{ \beta_0^g - c} f \right) + \pi \left( \int_{-\infty}^{ \beta^g_0 + \beta^g_1 - c} f \right), \end{multline}
 and so \begin{multline}\label{thm:gamma_expression_2} 1 - \E\left[\hat{p}_i\right] = (1 - \pi) + \pi - \E[\hat{p}_i]  = (1-\pi) \left(1 - \int_{c - \beta_0^g}^\infty f \right)  + \pi \left(1 - \int_{c - \beta^g_0 - \beta^g_1}^\infty f \right) \\ = (1 - \pi) \left( \int_{-\infty}^{c - \beta^g_0} f \right) + \pi \left( \int_{-\infty}^{c - \beta_0^g - \beta_1^g} f \right).
\end{multline}
Next,
\begin{equation}\label{thm:gamma_expression_3}
\omega = \int_{c - \beta^g_1 - \beta^g_0}^\infty f,\end{equation} and so
\begin{multline}\label{thm:gamma_expression_4}
\omega - \E[\hat{p}_i]  = \left( \int_{c - \beta^g_1 - \beta^g_0}^\infty f \right) - (1 - \pi) \left( \int_{c - \beta^g_0}^\infty f \right) - \pi \left( \int_{c - \beta_0^g - \beta_1^g}^\infty f \right) \\ = (1 - \pi) \left(\int_{c - \beta^g_0 - \beta^g_1 }^\infty f \right) - (1- \pi) \left(\int_{c - \beta^g_0}^\infty f \right) \\ =  (1 - \pi)\left(\int_{-\infty}^{\beta_0^g + \beta_1^g - c} f \right) - (1 - \pi) \left( \int_{-\infty}^{ \beta_0^g - c} f \right).
\end{multline}
Combining (\ref{thm:gamma_expression_1}, \ref{thm:gamma_expression_2}, \ref{thm:gamma_expression_3}, \ref{thm:gamma_expression_4}), we find that
\begin{multline}\label{gamma_alternative}
\gamma(\beta^g_1, c, \pi) = \frac{\pi(\omega - \E[\hat{p}_i])}{\E[\hat{p}_i](1 - \E[\hat{p}_i])} \\ = \frac{\pi \left[ (1 - \pi) \left( \int_{ -\infty}^{\beta_0^g + \beta_1^g - c} f \right) - (1 - \pi) \left( \int_{-\infty}^{ \beta_0^g - c} f \right) \right]}{\left[(1-\pi) \left( \int_{-\infty}^{ \beta_0^g - c} f \right) + \pi \left( \int_{-\infty}^{ \beta^g_0 + \beta^g_1 - c} f \right) \right] \left[(1 - \pi) \left( \int_{-\infty}^{c - \beta^g_0} f \right) + \pi \left( \int_{-\infty}^{c - \beta_0^g - \beta_1^g} f \right) \right]}.
\end{multline}
As a corollary, when $\pi = 1/2$,
\begin{multline}\label{gamma_alternative_pi_half}
\gamma(\beta^g_1, c, 1/2)  \\ = \frac{\left( \int_{ -\infty}^{\beta_0^g + \beta_1^g - c} f \right) - \left( \int_{-\infty}^{ \beta_0^g - c} f \right) }{ \left[ \left( \int_{-\infty}^{ \beta_0^g - c} f \right) + \left( \int_{-\infty}^{ \beta^g_0 + \beta^g_1 - c} f \right) \right] \left[\left( \int_{-\infty}^{c - \beta^g_0} f \right) + \left(\int_{-\infty}^{c - \beta_0^g - \beta_1^g} f \right) \right]}.
\end{multline}
Recalling the definitions of $g$ (\ref{def_g}) and $h$ (\ref{def_h}), we can write $\gamma$ as
$$ \gamma(\beta^g_1, c, \pi) = \frac{\pi g(\beta^g_1, c, \pi)}{h(\beta^g_1, c,\pi)}.$$

@@

We compute the derivatives of $g$ and $h$ in $c$, which we will need to prove subsequent results. First, by FTC and the evenness of $f$, we have that
\begin{multline}\label{dg_dc}
D_2 g(\beta^g_1, c, \pi) = -(1-\pi)f( \beta^g_0 + \beta^g_1 - c ) + (1-\pi) f(\beta^g_0 - c) \\ = (1-\pi) f(c - \beta^g_0) - (1-\pi)f(c - \beta^g_0 - \beta^g_1).
\end{multline}
Second, we have that
\begin{multline}\label{dh_dc}
D_2 h(\beta^g_1, c, \pi) \\ = -[(1-\pi)f(\beta^g_0 - c) + \pi f( \beta^g_0 + \beta^g_1 - c )]\left[(1-\pi)\left(\int_{-\infty}^{c - \beta^g_0} f \right) + \pi \left(\int_{-\infty}^{c - \beta_0^g - \beta_1^g} f \right) \right] \\ + [(1-\pi) f(c - \beta^g_0) +  \pi f(c - \beta^g_0 - \beta^g_1)] \left[(1-\pi)\left( \int_{-\infty}^{\beta_0^g - c} f \right) + \pi \left(\int_{-\infty}^{ \beta^g_0 + \beta^g_1 - c} f \right) \right] \\ = \left[ (1-\pi) f(c - \beta^g_0) +  \pi f(c - \beta^g_0 - \beta^g_1) \right] \cdot \\ \bigg[ (1-\pi)\left( \int_{-\infty}^{\beta_0^g - c} f \right) + \pi \left(\int_{-\infty}^{ \beta^g_0 + \beta^g_1 - c} f \right) \\ - (1-\pi)\left(\int_{-\infty}^{c - \beta^g_0} f \right) - \pi \left(\int_{-\infty}^{c - \beta_0^g - \beta_1^g} f \right) \bigg].
\end{multline}

\subsubsection{Limit of $\gamma$ in $c$}

Assume (without loss of generality) that $\beta^g_1 > 0$. We compute $\lim_{c \to \infty} \gamma(\beta^g_1, c, \pi)$. Observe that $$\lim_{c \to \infty} g(\beta^g_1, c, \pi) = \lim_{c \to \infty} h(\beta^g_1, c, \pi)  = 0.$$ Therefore, we can apply L'H\^{o}pital's rule. We have by (\ref{dg_dc}) and (\ref{dh_dc}) that \begin{multline}\label{c_limit_product}
\lim_{c \to \infty} \gamma(\beta^g_1, c, \pi) = \lim_{c \to \infty} \frac{\pi D_2 g(\beta^g_1, c, \pi)}{D_2h(\beta^g_1, c, \pi)} \\ = \lim_{c \to \infty} \bigg\{ \frac{(1-\pi) f(c - \beta^g_0) + \pi f(c - \beta^g_0 - \beta^g_1)}{\pi (1-\pi) f(c - \beta^g_0) - \pi (1-\pi)f(c - \beta^g_0 - \beta^g_1)} \\ \cdot \bigg[ (1-\pi)\left( \int_{-\infty}^{\beta_0^g - c} f \right) + \pi \left(\int_{-\infty}^{ \beta^g_0 + \beta^g_1 - c} f \right) \\ - (1-\pi)\left(\int_{-\infty}^{c - \beta^g_0} f \right) - \pi \left(\int_{-\infty}^{c - \beta_0^g - \beta_1^g} f \right) \bigg] \bigg\}^{-1}.
 \end{multline}
 We evaluate the two terms in the product (\ref{c_limit_product}) separately. First, observe that
 \begin{equation}\label{c_limit_product_2}
 \frac{(1-\pi) f(c - \beta^g_0) + \pi f(c - \beta^g_0 - \beta^g_1)}{\pi (1-\pi) f(c - \beta^g_0) - \pi (1-\pi)f(c - \beta^g_0 - \beta^g_1)} = \frac{\frac{(1-\pi) f(c - \beta^g_0)}{ f(c - \beta^g_0 - \beta^g_1)} + \pi}{\frac{ \pi(1-\pi) f(c - \beta^g_0)}{ f(c - \beta^g_0 - \beta^g_1)} - \pi(1-\pi)}.
 \end{equation}
 To evaluate the limit of (\ref{c_limit_product_2}), must evaluate the limit of
 \begin{multline}\label{c_limit_product_3}
 \frac{f(c - \beta^g_0)}{f(c - \beta^g_0 - \beta^g_1)} = \frac{\exp{[-(1/2)(c - \beta_0^g)^2]}}{\exp{[-(1/2)( c - \beta^g_0 - \beta^g_1)^2]}} \\ = \frac{\exp[ -(1/2)(c^2 - 2 c \beta^g_0 + (\beta^g_0)^2)]}{\exp\left[-(1/2)( c^2 - 2c \beta^g_0 - 2 c \beta^g_1 + (\beta^g_0)^2 + 2( \beta^g_0 \beta^g_1) + (\beta^g_1)^2)\right]} \\ = \exp\big[-c^2/2 + c \beta^g_0 - (\beta^g_0)^2/2 \\ + c^2/2 - c \beta^g_0 - c \beta^g_1 + (\beta^g_0)^2/2 + \beta^g_0 \beta^g_1 + (\beta^g_1)^2/2 \big] \\ = \exp[ -c \beta^g_1 + \beta^g_0 \beta^g_1 + (\beta^g_1)^2/2] = \exp[ \beta^g_0 \beta^g_1 + (\beta^g_1)^2/2]\exp[ -c \beta^g_1]. 
\end{multline}
Computing the limit of (\ref{c_limit_product_3}), we obtain
$$
\lim_{c \to \infty} \frac{f(c - \beta^g_0)}{f(c - \beta^g_0 - \beta^g_1)} = \exp[ \beta^g_0 \beta^g_1 + (\beta^g_1)^2/2] \lim_{c \to \infty} \exp[ -c \beta^g_1] = 0
$$ for $\beta^g_1 > 0$. We now can evaluate the limit of (\ref{c_limit_product_2}) (for $\beta^g_1 > 0$):
$$ \lim_{c \to \infty} \frac{(1-\pi) f(c - \beta^g_0) + \pi f(c - \beta^g_0 - \beta^g_1)}{\pi (1-\pi) f(c - \beta^g_0) - \pi (1-\pi)f(c - \beta^g_0 - \beta^g_1)} = \frac{-\pi}{\pi(1-\pi)} = -\frac{1}{1 -\pi}.$$ Next, we compute the limit of the other term in the product (\ref{c_limit_product}):
\begin{multline}\label{c_limit_product_4}
\lim_{c \to \infty} \bigg[ (1-\pi)\left( \int_{-\infty}^{\beta_0^g - c} f \right) + \pi \left(\int_{-\infty}^{ \beta^g_0 + \beta^g_1 - c} f \right) \\ - (1-\pi)\left(\int_{-\infty}^{c - \beta^g_0} f \right) - \pi \left(\int_{-\infty}^{c - \beta_0^g - \beta_1^g} f \right) \bigg] = -(1-\pi) - \pi = -1.
\end{multline}
Combining (\ref{c_limit_product_2}) and (\ref{c_limit_product_4}), the limit (\ref{c_limit_product}) evaluates to
$$ \lim_{c \to \infty} \gamma(\beta^g_1, c, \pi) = \left(  \frac{ 1 }{ 1 - \pi }\right)^{-1} = 1 - \pi.$$ It follows that the limit in $c$ of the bias $b$ is
$$\lim_{c \to \infty} b(\beta^g_1, c, \pi) = \beta_1^m(1 - \lim_{c \to \infty} \gamma(\beta^g_1, c, \pi)) = \beta^m_1 \pi.$$
A corollary is that
$$\lim_{c \to \infty} b(\beta^g_1, c, 1/2) = (1/2)\beta^m_1.$$

\subsubsection{Critical values of }
